---
title: "3_3_Indices_Ancestria"
author: "Idalia Rojas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Requerimentos

-   tess3
-   tydiverse
-   devtools
-   maps
-   LEA

```{r installation}
# install.packages("devtools")
#devtools::install_github("bcm-uga/TESS3_encho_sen")
#install.packages("maps")
#if (!require("BiocManager", quietly = TRUE))
  
#    install.packages("BiocManager")

#BiocManager::install("LEA")
```

Call libraries

```{r libraries}
library(maps)
library(tess3r)
library(LEA)
```

## Indices de ancestria

Los indices de ancestria son un analisis de agrupamiento no supervisado que emplea el metodo de K-means. En este tutorial emplearemos la paqueteria de R `Tess3` <https://bcm-uga.github.io/TESS3_encho_sen/articles/main-vignette.html>

Transformar nuestro archiv en el archivo de genotipos que emplea tss3

```{r formato}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
